Figures

### 2021-08-10 manuscript/figures.Rmd
sync figures Rmd with submitting ms

\arrayrulecolor{white}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", dev = c("pdf"))
knitr::opts_chunk$set(fig.pos = 'H')
```

@@

>>>>

\arrayrulecolor{white}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", dev = c("pdf"))
knitr::opts_chunk$set(fig.pos = "H")
```

@@

```{r 00_map_bathy, fig.cap = "Map of study lakes showing A) lake e maximum depth measurements, B) cross-section shape class, and C) reservoir classification. The distribution of lake depths from panel A is reported in Figure S4.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/00_map_bathy-1.pdf")
```

\vspace{5em}
